\section{Introduction}
The need to locate people and objects as soon as possible has always been an important part of any organization or industry. With use of wireless technology, we are trying to remotely locate objects within a predefined time frame. \gls{gps} is obviously the most widely used outdoor location sensing technology, but there are several drawbacks which make \gls{gps} impossible to be used as an indoor positioning system with high precision. Due to line-of-sight demand between the satellites and the receiver, and specialized hardware requirement, it has poor indoor coverage and insufficient accuracy\cite{Insufficient}. 

We typically use small low-power transceiver attached to assets as well as sets of readers that map the location of these assets. Systems that map a location relative to a fixed set of coordinates are more accurately called \gls{rtls}. Wireless \gls{rtls} tags are attached to objects or worn by people, and in most \gls{rtls}, fixed reference points receive wireless signals from tags to determine their location. \gls{rtls} is one of the latest solutions for tracking objects in real time with high precision. \gls{rtls} has many advantages and can be combined with different technologies depending in which it is being applied. This is the type of system that we are looking to build first and implement it to automate the driving license trial system.


\subsection{Objectives}
The major objectives behind trying to build this system is to replace traditional human inspection based method of giving license to the drivers in the license trial.  
\begin{enumerate}
\item To fulfill the course requirement.
\item To apply the knowledge gained in engineering tenure in an useful project.
\item To learn the implementation of Real Time Location System.
\item To automate the license trial system.
\item To eliminate the errors in current trial system.

\end{enumerate}


\subsection{Statement of Problem}
Using real time location system, we aim to automate the license trial system. The real time path followed by the vehicle is tracked using the \gls{rtls}. The track followed by the vehicle should be within some limit in the real trial system. In this project, we put ultrasonic transmitters on the vehicle subjected to trial and we also place three ultrasonic receivers in three predefined location, which receive the ultrasonic signal transmitted by the transmitter in the vehicle. The time taken by the signal to travel from transmitter to receiver along the air can be used to find the distance between the transmitter and receiver. From this distance, the position of the vehicle can be identified. And by using the information of the path followed by the vehicle using \gls{rtls}, it can be judged whether the path followed by the vehicle was within the trial track. The major goal of this project is to actually judge whether the vehicle followed the correct path. 


\subsection{Motivation}
Statistics reveal the death of great number of people and loss of huge property due to the increasing road accidents. Studies have attributed the major cause of road accidents to drivers in charge of safety of passengers. Even the licenced drivers have been found guilty of major road accidents if not people who are not authorized to drive. 


In a regular basis lots of people are dead without having to do any error of their own but just because the unlucky vehicle they happened to be was driven by unskilled drivers.


It has already been shown that the driving license trial system has a flaw, human error of inspection may lead to granting of driving license to non-skilled drivers. Something has to be instantly done to address such severe condition. 


We, the engineering students, have come up with certain ideas to eliminate the situation. What we could do from our perspective is to contribute with a automatic system to replace the license trial system. 
